### 2019-11-12 cvpr_submission/related_work.tex
Merged the "imported" related work section with the newer one.

\section{Related work -- import}
%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.  Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.

@@

Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}. 
Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g. object disappearance).
To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

@@

\section{Related work}
Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.  Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations. Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.

Another research focus area has been multimodal fusion and
attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
features \cite{zhou2015simple, antol2015}.  Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .  Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.   Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.   Visualization of attention steps also provide interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach.  The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.  Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .  Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.   These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.  Learning long-term dependencies is also another challenge that LSTMs may struggle with.  Yin et al. 2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input.  Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.  Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history. However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

>>>>

\section{Related work}
%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.  Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.

@@

Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.  Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, most datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations. Prior work generally relied on dense visual features produced by either CNNs~\cite{xiong2016dynamic,yang2016stacked} or object detection modules~\cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings~\cite{teney2017graph, santoro2017simple}.

A variety of new tasks integrating vision and language have appeared in the past several years~\cite{mogadala2019trends}.
Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) as well as temporal aspects and relations (e.g. object disappearance).
Earlier work~\cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video. These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.  Learning long-term dependencies is also another challenge that LSTMs may struggle with. Yin et al.~\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.

% Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
Another research focus area has been multimodal fusion and attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal features \cite{zhou2015simple, antol2015}.  Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}.  Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.   Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.   Visualization of attention steps also provide interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach.  The follow-up model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.  Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.

@@

%Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .  
Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input.
Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.  Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history. However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
